Blum axioms and nondeterministic computation of functions

### 2016-04-20 paper.tex
paper.tex: Simplify the introduction of the "Quality Standards" section.

In the context of deciders,
allowing doubly-infinite tapes and multiple tapes,
although simplifies the design and increases the efficiency of the machine,
does not expand the class of languages that can be decided or recognized by the machine.
That is, both models are \emph{computationally equivalent}.
Therefore,
our definition must produce an equivalent model
--- every function that can be computed by deterministic means
must be computable under our new definition and vice-versa.
This is the ``computation'' part.

But nondeterministic deciders,
although computationally equivalent to deterministic ones,
are apparently exponentially faster.
That is, while we have linear-time non-deterministic algorithms for Boolean satisfiability,
the best known deterministic algorithms are still exponential in the worst case.
Nondeterminism seems special in this sense;
although other extensions (multiple tapes and doubly-infinite tapes)
can be simulated under just a polynomial slowdown,
the simulation of nondeterminism seems to require exponential slowdown.%
\footnote{
    Simulating nondeterminism under a polynomial slowdown would show that $\P = \NP$;
    showing that the slowdown must be exponential would show that $\P \neq \NP$.
    Although most researchers expect the later to be the case~\cite[p.~54]{Gasarch2012},
    as Papadimitriou noted~\cite[p.~412]{Papadimitriou1994},
    in the absence of a proof that $\P \neq \NP$
    we should not be too emphatic in stating the simulation \emph{require}
    (as opposed to \emph{seemingly require}) exponential slowdown.
}
Therefore,
our definition must exhibit this apparent exponential speedup
when computing, for instance, the characteristic function\footnotemark{} of $\SAT$.
\footnotetext{
    The characteristic function of a set $A$
    is the function $1_A$ defined by
    \begin{equation*}
        1_A(x) = \begin{cases}
            1, & \text{if $x \in A$}. \\
            0, & \text{if $x \notin A$}.
        \end{cases}
    \end{equation*}
}
This is the ``non-deterministic'' part.

Section~\ref{sec:godel-numberings}
presents a formalization of the ``computation'' part
and section~\ref{sec:blum-axioms}
presents a formalization of the ``non-deterministic'' part.

>>>>

In the ``computation'' part,
we want not to fall in the realm of undecidable problems,
but neither we want to ``forget'' of some computable function.
Therefore,
the new definition must be \emph{computationally equivalent}
to the deterministic machines.

In the ``non-deterministic'' part,
we want to preserve the fact that
converting to deterministic machines seems
\footnote{
    Simulating nondeterminism under a polynomial slowdown would show that $\P = \NP$;
    showing that the slowdown must be exponential would show that $\P \neq \NP$.
    Although most researchers expect the later to be the case~\cite[p.~54]{Gasarch2012},
    as Papadimitriou noted~\cite[p.~412]{Papadimitriou1994},
    in the absence of a proof that $\P \neq \NP$
    we should not be too emphatic in stating the simulation \emph{require}
    (as opposed to \emph{seemingly require}) exponential slowdown.
}
to require an exponential slowdown.
Therefore,
our definition must exhibit this apparent exponential speedup
when computing, for instance, the characteristic function\footnotemark{} of $\SAT$.
\footnotetext{
    The characteristic function of a set $A$
    is the function $1_A$ defined by
    \begin{equation*}
        1_A(x) = \begin{cases}
            1, & \text{if $x \in A$}. \\
            0, & \text{if $x \notin A$}.
        \end{cases}
    \end{equation*}
}
This is the ``non-deterministic'' part.

Sections \ref{sec:godel-numberings} and~\ref{sec:blum-axioms}
formalize our requirements for the ``computation'' part
and the ``non-deterministic'' part,
respectively.
